Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

>>>>

The measurements we have done in the simulations can be compared
against observational results.
We use the observational constraints by \cite{LM10} and \cite{Bovy16}
to place our results in an observational context.
\cite{LM10} used observations of the long Sagittarius tidal stream to
constrain the shape of the gravitational potential.
Their point of depart is that previous studies that assumed an
axisymetric Galactic potential were not able to fit all the available
dynamic constraints for the Sagittarius stream, therefore they
proposed a rigid triaxial potential, with coaxial potential
ellipsoids, for the dark matter component.  
Their results are able to constrain the triaxility of this potential
component, translating these results into a triaxiality of the density
contours they report $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of
$\sim 40$kpc. They do not report any uncertainties for these two
values. 
Looking at their plots of their quality of fit criterion as a function
of dark halo axial scales (Figure 5), we choose a conservative $10\%$
relative uncertainty, close to the uncertainty in those parameters.
The element that made the results by \cite{LM10} (LM10 hereafter) surprising is that
the minor axis of the halo shape is parallel, not perpendicular, to
stellar disk plane.

The results by \cite{Bovy16} (BBFK16 hereafter) have the same general approach but use
instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
streams to constraint the shape of the dark matter component of the
galacic halo potential.
They use general models with large degrees of freedom for the galactic
potential in order to measure to what extent these two streams are sensitive
to the triaxiality of the dark matter halo component.
The DM component is written directly as a triaxial density profile
with coaxial ellipsoids and the corresponding potential is found by
numerical integration.
They find that the width of the Pal 5 stream constraints $b/a\approx
1$ and therefore fix it to $b/a=1$, finally they report their most stringent
constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
Pal 5 stream.

Our Figure \label{fig:observations} shows an explicit comparison in
the $c/a$-$b/a$ plane of the results by LM10
